---
title: HW2
author: Miracle Ephraim
format:
  pdf:
    documentclass: article
---

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stringr, readxl, data.table, gdata)
library(ggplot2)
library(dplyr)
library(MatchIt)
library(WeightIt)
library(sandwich)
library(lmtest)
library(tibble)
library(knitr)
library(tidyr)
load("C:/Users/mirac/Documents/GitHub/econ470_ma/hw2/submission/hw_workspace.Rdata")
print(ls()) 

```

1. Hospital reports over time
```{r} 
#| echo: false
ggplot(data = total_report_count, aes(x=year, y=total)) +
     geom_line()

```

2. Number of unique hospital ids
```{r}
#| echo: false
total_report_count <- hospital_report_counts %>%
     group_by(year) %>%
     summarise(total = n())

tibble(Unique_hospital_ids = nrow(total_report_count))

```

3. Distribution of total charges
```{r}
#| echo: false
ggplot(final_HCRIS_data_new, aes(x = factor(year), y = tot_charges)) +
  geom_violin(scale = 'width') +
  scale_y_continuous(trans='log10')

```

4. Distribution of price
```{r}
#| echo: false
ggplot(final_HCRIS_data_new, aes(as.factor(year), price)) +
  geom_violin(scale = 'width') +
  scale_y_continuous(trans='log10')
```

5. Average prices of penalized and non-penalized hospitals
```{r}
#| echo: false
HCRIS_2012 %>%
filter(penalty > 0) %>%
group_by(year) %>%
summarize(avg_price_nopen = mean(price))

HCRIS_2012 %>%
filter(penalty == 0) %>%
group_by(year) %>%
summarize(avg_price_pen = mean(price))

```

6. Bed size quantiles and their average prices
```{r}
#| echo: false
kable(final_table, caption = "Average Price by Bed Quartile Group")


```

7. Calculating different estimators
```{r}
#| echo: false
kable(estimands_table, caption = "Estimated Treatment Effects by Method")

```

8. Each of these estimators produce very different estimates. 
9. Due to the limited number of penalized hospitals in the dataset, I do not believe the causal effect was properly captured. 
10. For some reason, working with this data was difficult because running the same code with different people was producing different outputs, which was kind of frustrating. 